Data preparation B

### 2020-01-13 script/data-prep-B.Rmd
agregar estatus subjetivo
v46 es la variable en cl99

dat99$redis <-rec(cl99$v35, rec="8:9=NA;else=copy")
dat99$redis <-rec(dat99$redis, rec="rev")
freq(dat99$redis)
dat99$redis <-set_labels(dat99$redis,labels= c("Muy en desacuerdo"=1, "En descacuerdo"=2,"Ni acuerdo ni desacuerdo"=3, "De acuerdo"=4, "Muy de acuerdo"=5))
get_labels(dat99$redis, values="as.name")
freq(to_label(dat99$redis))
```

>>>>

dat99$redis <-rec(cl99$v35, rec="8:9=NA;else=copy")
dat99$redis <-rec(dat99$redis, rec="rev")
freq(dat99$redis)
dat99$redis <-set_labels(dat99$redis,labels= c("Muy en desacuerdo"=1, "En descacuerdo"=2,"Ni acuerdo ni desacuerdo"=3, "De acuerdo"=4, "Muy de acuerdo"=5))
get_labels(dat99$redis, values="as.name")
freq(to_label(dat99$redis))
```
### e - estatus subjetivo
